Best Practices for Single Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-06-27 paper/manuscript.tex
clarify statement about restraints and open-source workflows

Recently, degrees of freedom for binding site and auxiliary potentials based on larger sets of atomic positions of the receptor and ligand have been put forward.
Fu et al. suggested restraining the six relative rigid-body degrees of freedom derived by finding the rotation of the ligand, which minimises the RMSD to a reference structure of the receptor-ligand complex (after accounting for rotation and translation of the receptor)~\cite{fu2017new}. Salari et al. proposed restraining the ``distance-from-bound-configuration'' (DBC) variable, which is the RMSD of ligand coordinates in the frame of reference of the binding site~\cite{salari2018streamlined, ebrahimi2022symmetry}. DBC may allow the binding pose to be closely preserved as the ligand intermolecular interactions are removed, but has the disadvantage of coupling the internal and relative external degrees of freedom of the receptor and ligand, making them unsuitable for describing the binding site macrostate and the corresponding standard state terms. However, these restraints are practical as auxiliary restraints when additional steps are used to introduce and release them. Moreover, because they are based on flat-bottom potentials encompassing the desired binding poses, the free energy of releasing them in the bound state can be safely neglected in most cases. DBC restraint schemes are implemented in open-source workflows~\cite{fu2021bfee2, fu2022accurate, santiago-mcrae2023computing, clark2023comparison, hedges2023suite}.

>>>>

Recently, degrees of freedom for binding site and auxiliary potentials based on larger sets of atomic positions of the receptor and ligand have been put forward.
Fu et al. suggested restraining the six relative rigid-body degrees of freedom derived by finding the rotation of the ligand, which minimises the RMSD to a reference structure of the receptor-ligand complex (after accounting for rotation and translation of the receptor)~\cite{fu2017new}. Salari et al. proposed restraining the ``distance-from-bound-configuration'' (DBC) variable, which is the RMSD of ligand coordinates in the frame of reference of the binding site~\cite{salari2018streamlined, ebrahimi2022symmetry}. DBC may allow the binding pose to be closely preserved as the ligand intermolecular interactions are removed, but has the disadvantage of coupling the internal and relative external degrees of freedom of the receptor and ligand, making them unsuitable for describing the binding site macrostate and the corresponding standard state terms. However, these restraints are practical as auxiliary restraints when additional steps are used to introduce and release them. Moreover, because they are based on flat-bottom potentials encompassing the desired binding poses, the free energy of releasing them in the bound state can be safely neglected in most cases. The restraint schemes discussed here are implemented in open-source workflows~\cite{fu2021bfee2, fu2022accurate, santiago-mcrae2023computing, clark2023comparison, hedges2023suite}.
